\setuppapersize[letter]

\setupbodyfont[dejavu-condensed,sans,8pt]

\setuppagenumbering
  [location={footer,inleft}]

\setupinteraction
  [state=start,
   color=,
   contrastcolor=,
   style=]

\setuplayout
  [% horizontal
   backspace=2.5in,
   leftmargin=1.75in,
   leftmargindistance=0.25in,
   width=5.5in,
   rightmargin=0in,
   % vertical
   topspace=0pt,
   header=1.2in,
   headerdistance=.1in,
   height=middle,
   footerdistance=0pt,
   footer=\lineheight,
   bottomspace=.5in]

\setupmarginblock
  [location=left,
   width=\leftmarginwidth,
   align={flushright,broad}]

\definelayer
  [pagebackground]
  [x=0pt,
   y=0pt,
   width=\paperwidth,
   height=\paperheight]

\setupbackgrounds
  [page]
  [background=pagebackground]

\defineitemgroup
  [timeline]
  [before={\blank[back]},
   inbetween=,
   width=6em]

\setuplines[before=,after=]

\define[1]\heading{%
  \dontleavehmode{\bfb\setupinterlinespace\strut#1}%
  \blank[small,samepage]
}
\define[1]\subheading{%
  \dontleavehmode{\bfa\setupinterlinespace\strut#1}%
  \blank[small,samepage]
}

\starttext

\setlayerframed
  [pagebackground]
  []
  [background=color,
   framecolor=darkgray,
   backgroundcolor=darkgray,
   foregroundcolor=white,
   width=\paperwidth,
   height=\dimexpr\topspace+\headerheight\relax]
  {%
    \dontleavehmode{\tfd john\bold{smith}}\blank[medium]
    junior business analyst
  }

\startmarginblock
  \heading{contact}
  \startlines
    123 Broadway
    City, State 12345
    Country
    ~
    +0 (000) 111 1111
    +0 (000) 111 1112
    ~
    \goto{john@smith.com}[url(mailto:john@smith.com)]
    \goto{http://www.smith.com}[url(http://www.smith.com)]
    \goto{fb://jsmith}[url(http://facebook.com/johnsmith)]
  \stoplines

  \heading{languages}
  \startlines
    english mother tongue
    spanish \& italian fluency
  \stoplines

  \heading{programming}
  \startlines
    \color[red]{♥} JavaScript
    Python, C++, PHP
    CSS3 \& HTML5
  \stoplines
\stopmarginblock

\heading{\color[cyan]{edu}cation}

\starttimeline
\sym{2011--2012} \bold{Masters} of Commerce\hfill
  \color[darkgray]{\tfx The University of California, Berkeley}

  \emph{Money Is The Root Of All Evil -- Or Is It?}

  This thesis explored the idea that money has been the cause of
  untold anguish and suffering in the world. I found that it has, in
  fact, not.

\sym{2007--2008} \bold{Bachelor} of Business Studies\hfill
  \color[darkgray]{\tfx The University of California, Berkeley}

  Specialization in Commerce
\stoptimeline

\heading{\color[magenta]{exp}erience}

\subheading{Full Time}

\starttimeline
\sym{2012--Now} \bold{LEHMAN BROTHERS}\hfill
  \color[darkgray]{\tfx Los Angeles, California}

  \emph{1\high{st} Year Analyst}

  Developed spreadsheets for risk analysis on exotic derivatives on a
  wide array of commodities (ags, oils, precious and base metals),
  managed blotter and secondary trades on structured notes, liaised
  with Middle Office, Sales and Structuring for bookkeeping.\par
  Detailed achievements:
  \startitemize[packed]
  \item Learned how to make amazing coffee
  \item Finally determined the reason for PC LOAD LETTER:
    \startitemize[packed]
    \item Paper jam
    \item Software issues:
      \startitemize[packed]
      \item Word not sending the correct data to printer
      \item Windows trying to print in letter format
      \stopitemize
    \item Coffee spilled inside printer
    \stopitemize
  \item Broke the office record for number of kitten pictures in cubicle
  \item Learned how to make more amazing coffee on a new machine
  \stopitemize
\stoptimeline

\subheading{Part Time}

\starttimeline
\sym{2010--2011} \bold{LEHMAN BROTHERS}\hfill
  \color[darkgray]{\tfx London, United Kingdom}

  \emph{Summer Intern}

  Received pre-placed offer from the Exotics Trading Desk as a result
  of very positive reviews. Rated "truly distinctive" for Analytical
  Skills and Teamwork.

\sym{2008-2009} \bold{Buy More}\hfill
  \color[darkgray]{\tfx Burbank, California}

  \emph{Computer Repair Specialist}

  Worked in the Nerd Herd and helped to solve computer problems by
  asking customers to turn their computers off and on again.
\stoptimeline

\heading{\color[orange]{awa}rds}

\starttimeline
\sym{2011} \bold{Postgraduate Scholarship}\hfill
  \color[darkgray]{\tfx School of Business, The University of California}

  Awarded to the top student in their final year of a Bachelors
  degree. Mastered the art of filing accurate TPS reports.
\stoptimeline

\heading{\color[green]{com}munication skills}

\starttimeline
\sym{2011} \bold{Oral Presentation}\hfill
  \color[darkgray]{\tfx California Business Conference}

  Presented the research I conducted for my Masters of Commerce
  degree.

\sym{2010} \bold{Poster}\hfill
  \color[darkgray]{\tfx Annual Business Conference, Oregon}

  As part of the course work for BUS320, I created a poster analyzing
  several local businesses and presented this at a conference.
\stoptimeline

\heading{\color[red]{int}erests}

\bold{professional:} data analysis, company profiling, risk analysis,
economics, web design, web app creation, software design, marketing
\bold{personal:} piano, chess, cooking, dancing, running

\stoptext